Mental Simulation as Bayesian Quadrature

### 2013-05-31 man/nips-2013.tex
Update caption

\begin{figure}[t]
  \centering
  \includegraphics[width=0.95\textwidth]{../figures/shepard-rotation.png}
  \caption{\textbf{Classic mental rotation task}. Participants in
    \cite{Shepard1971} saw stimuli such as these, and judged whether
    each pair of shapes was the same shape in two different
    orientations, or two different shapes. \textbf{A} shows a ``plane
    rotation'', \textbf{B} shows a ``depth rotation'', and \textbf{C}
    shows two distinct objects. \TODO{update this caption}}
  \label{fig:mental-rotation}
\end{figure}

>>>>

\begin{figure}[t]
  \centering
  \includegraphics[width=0.8\textwidth]{../figures/shepard-rotation.png}
  \caption{\textbf{Classic mental rotation task}. Participants in
    \cite{Shepard1971} saw stimuli such as those on the left, and
    judged whether each pair of shapes was the same shape in two
    different orientations (``same'' pairs), or two different shapes
    (``different'' pairs). \textbf{A} and \textbf{B} show ``same''
    pairs, while \textbf{C} shows a ``different'' pair. The plots on
    the right indicate mean response times on the mental rotation
    task, exhibiting a strong linear relationship with increasing
    variance as a function of true rotation.}
  \label{fig:mental-rotation}
\end{figure}
